Labour

### 2023-02-21 docsrc/documentation/notebooks/labour.Rmd

---
title: "Labour"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

@@

```{r labour_output, echo=FALSE}
options(width=120)
nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds")
nnet_confusion_matrix("../../../data/transitions/test/labour_nnet_2018_2019.rds", mode='multinom', 'factor(labour_state_next)')
```

>>>>

---
title: "Labour"
output: html_document
bibliography: 
  #- "docsrc/refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  - "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

```{r setup, include=FALSE}
#knitr::opts_knit$set(root.dir= "../minos")
```

```{r load_data, include=FALSE}
source('docsrc/documentation/notebooks/sphinx_notebook_utils.R')
```

@@

```{r labour_output, echo=FALSE}
options(width=120)
#nnet_output("data/transitions/labour/nnet/labour_nnet_2018_2019.rds")
nnet_confusion_matrix("data/transitions/labour/nnet/labour_nnet_2018_2019.rds", mode='multinom', 'labour_state_next')
```
